Query Optimization for Dynamic Imputation

### 2017-05-12 paper/experiments.tex
paper: remove extra paragraph
removed panning time plot, mentioned reductions in text

\subsubsection{Planning Times}
\begin{figure}
\centering
\includegraphics[scale=0.4]{figures/planning_times_plot.png}
\caption{Planning times are sub-second for up to 5 joins. For more joins, we implement an approximation to Pareto sets. Users can increase the level of
approximation for more aggressive planning reductions.
}
\label{fig:planning-times}
\end{figure}

@@

However, \ProjectName{}'s planning algorithm is still exponential in the number of joins in the plan, and the use of Pareto sets exacerbates this exponential growth.
We explored the limits of our planning algorithm by constructing a series of queries with increasing number of joins over the CDC tables.
Planning times (~\Cref{fig:planning-times}) for queries involving 1--5 joins---a practical value for a practical subset of real world exploratory queries---are less than 1 second.
We extended \ProjectName{} to support an approximation of Pareto sets to improve planning times for queries with 6 or more joins. Approximate Pareto sets
displayed a reduction in planning time linear with respect to the reduction in size of the final frontier. Users can increase the level of approximation to reduce planning times further.
%\todobox{Jose: I'm not a fan of this line, I would remove}{Furthermore, at that point, it may make more sense to specify a coherent model over the entire base table instead.}

>>>>

%\subsubsection{Planning Times}
%\begin{figure}
%\centering
%\includegraphics[scale=0.4]{figures/planning_times_plot.png}
%\caption{Planning times are sub-second for up to 5 joins. For more joins, we implement an approximation to Pareto sets. Users can increase the level of
%approximation for more aggressive planning reductions.
%}
%\label{fig:planning-times}
%\end{figure}

@@

However, \ProjectName{}'s planning algorithm is still exponential in the number of joins in the plan, and the use of Pareto sets exacerbates this exponential growth.
We explored the limits of our planning algorithm by constructing a series of queries with increasing number of joins over the CDC tables.
Planning times (~\Cref{fig:planning-times}) for queries involving 1--5 joins---a practical value for  real world exploratory queries---are less than 1 second.
We extended \ProjectName{} to support an approximation of Pareto sets to improve planning times for queries with 6 or more joins. Approximate Pareto sets
displayed a reduction in planning time linear with respect to the reduction in size of the final frontier. For queries with 6--8 joins, approximate sets achieved a reduction
in planning time between 14\% and 23\%, on average. Users can increase the level of approximation to reduce planning times further.
%\todobox{Jose: I'm not a fan of this line, I would remove}{Furthermore, at that point, it may make more sense to specify a coherent model over the entire base table instead.}
